Formalizing the Kolmogorov extension Theorem in Lean

### 2023-09-12 Manuscript/proof_outline.tex
fix leanline spacing

    \item \sloppy In \leanline{Lean}, we have the \leanline{class
      PseudoEMetricSpace (α : Type u) extends EDist}, where

@@

      \leanline{∀ (s : Set α), IsOpen s ↔ ∀ (x : α), x ∈ s → {p |
          p.fst = x → p.snd ∈ s} ∈ uniformity}. In particular, a

@@

\noindent
Any ring is a semi-ring since $A\cap B = A \setminus (A \setminus B)$,
i.e.\ every ring is a $\pi$-system.
Using \leanline{variable {α : Type _} {s t : Set α}
}, we define a semi-ring as follows:

>>>>

    \item \sloppy In \leanline{Lean}, we have the \leanline{class PseudoEMetricSpace (α : Type u) extends EDist}, where

@@

      \leanline{∀ (s : Set α), IsOpen s ↔ ∀ (x : α), x ∈ s → {p | p.fst = x → p.snd ∈ s} ∈ uniformity}. In particular, a

@@

\noindent
Any ring is a semi-ring since $A\cap B = A \setminus (A \setminus B)$,
i.e.\ every ring is a $\pi$-system.
Using \leanline{variable {α : Type _} {s t : Set α}}, we define a semi-ring as follows:
